\documentclass{article}
\usepackage{kotex, geometry, hyperref, graphicx}

\title{Week 6 - HMI Research Group \\ \large 10 Jul 2017 - 14 Jul 2017}
\author{Long Phi Nguyen (뉀피롱), 한국전자통신연구원}

\begin{document}

  \pagenumbering{gobble}
  \maketitle


  \subsection*{Summary} The previous plan for generating new motions has been ruled out---the method of data collection and analysis
  was very brute-force-based, inaccurate, and did not take sequential data into account.
  As such, NAO fell down almost $100\%$ of the time when trying to generate
  new gestures aside from the \verb|BodyTalk| category. Time series analysis is in progress.

  \subsection*{Points}
  \begin{itemize}
    \item \verb|README.md| has been created on Github repository for documentation purposes.
    \item Reparsed NAO's sensor data to collect sensor data chronologically as he moves while performing \verb|BodyTalk| gestures.
    \item Wrote a function that calculates and plots the time series data for each of the \verb|BodyTalk| gestures.
    \item Noticed some general trends between certain groups of joints related to the \verb|BodyTalk| category, such as
          joint symmetry during interpolation, etc.
    \item Read through the USC paper regarding low-dimensional manifolds.
  \end{itemize}

  \subsection*{Plans}
  \begin{itemize}
    \item Come up with a preliminary method to work with the time series data and generate better gestures from it.
    \item Link data from gestures in a way that doesn't rely on brute-forcing them by skewed frequency (be smart about analysis).
    \item Set constraints on generated gestures so that transitions between successive gestures are smooth, not abrupt as they currently are.
    \item Refactor code for ease of understanding.
  \end{itemize}

  \subsection*{Addendum}
  The repository can be found \href{https://github.com/longnguyen1997/nao_animations}{\texttt{here}} with its updated \verb|README.md|.
  Time series plots for gestures from the \verb|BodyTalk| category can be found
  \href{https://github.com/longnguyen1997/nao_animations/tree/master/plots/time_series/standing_bodytalk}{\texttt{here}}.

\end{document}
