\documentclass{article}
\usepackage{kotex, geometry, hyperref}

\title{Week 2 - HMI Research Group \\ \large 8 Jun 2017 - 16 Jun 2017}
\author{Long Phi Nguyen (뉀피롱), 한국전자통신연구원}

\begin{document}

  \pagenumbering{gobble}
  \maketitle


  \subsection*{Summary} This week consisted of primarily getting used to applied learning machine methods and possible libraries to explore in preparation for doing work with the NAO robot. The NAOqi API was studied, given online documentation from Aldebaran.

  \subsection*{Points}
  \begin{itemize}
    \item Learned how to use the \verb|scikit-learn| Python library for machine learning.
    \item Read up on various parts of machine learning---neural networks, classification, regression.
    \item Studied Aldebaran documentation regarding the creation of new NAO modules in Python.
    \item Worked with the \verb|spaCy| Python NLP library to better understand how words are parsed and processed syntactically.
  \end{itemize}

  \subsection*{Plans}
  \begin{itemize}
    \item Feed inputs to NAO and have it learn what gestures it should perform based on processing of the given input.
    \item Compare models and determine which works best in learning and NLP.
    \item Work further with \verb|spaCy| and better understand how language works computationally.
    \item Get more familiar with \verb|scitkit-learn| and understand reinforcement learning.
  \end{itemize}

  \subsection*{Miscellaneous}
  Mini-projects worked on to apply methods learned can be found at \href{http://github.com/longnguyen1997}{\texttt{github.com/longnguyen1997}}. Projects are titled \verb|food_preferences| and \verb|ml_model_comparisons|.

\end{document}
